%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[10pt, a4paper, twocolumn]{article} % 10pt font size (11 and 12 also possible), A4 paper (letterpaper for US letter) and two column layout (remove for one column)
\linespread{1.1} % Line spacing
\input{structure} % Specifies the document structure and loads requires packages
%----------------------------------------------------------------------------------------
%	ARTICLE INFORMATION
%----------------------------------------------------------------------------------------
\title{Meta Defender} % The article title
\author{
	\authorstyle{alvin@metadefender.finance} % Authors
	\newline
	\authorstyle{angie@metadefender.finance}
	\newline
	\authorstyle{vincent@metadefender.finance}
	\newline\newline % Space before institutions
	%\textsuperscript{1}\institution{Universidad Nacional Autónoma de México, Mexico City, Mexico}\\ % Institution 1
	%\textsuperscript{2}\institution{University of Texas at Austin, Texas, United States of America}\\ % Institution 2
	%\textsuperscript{3}\institution{\texttt{LaTeXTemplates.com}} % Institution 3
}
\date{\today} % Add a date here if you would like one to appear underneath the title block, use \today for the current date, leave empty for no date
%----------------------------------------------------------------------------------------

\begin{document}

\maketitle % Print the title

\thispagestyle{firstpage} % Apply the page style for the first page (no headers and footers)

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

\lettrineabstract{The security industry is enormous and plays an important role in the traditional financial market.
However, the traditional insurance model does not work in the Web3 world because the claiming procedures are time-consuming and opaque.
Furthermore, one cannot enter the insurance industry efficiently because capital for underwriting is only available to the "Big Money".
MetaDefender serves as a pioneer in creating a permissionless platform for risk/insurance trading on-chain, allowing both underwriters and policy buyers to benefit from the blockchain's instant, convenient, and transparent service.
}

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\section{Background}\label{sec:background}
\input{paragraphs/background}

%------------------------------------------------

\section{Introduction}\label{sec:introduction}
\input{paragraphs/introduction}

%------------------------------------------------

\section{Solution Overview}\label{sec:solution-overview}
\input{paragraphs/solution-overview}

\section{Dynamic Pricing Model}\label{sec:dynamic-pricing-model}
\input{paragraphs/dynamic-pricing-model}

\section{Epoch Management}\label{sec:epoch-management}
\input{paragraphs/epoch-management}

\section{Risk Reserve}\label{sec:risk-reserve}
\input{paragraphs/risk-reserve}

\section{DAO}\label{sec:dao}
\input{paragraphs/DAO}
%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------
\printbibliography[title={Bibliography}] % Print the bibliography, section title in curly brackets
\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template
\bibitem[Marcus, Alan and Shaked, Israel, 1984]{Marcus et al., 1984}
Marcus, Alan and Shaked, Israel.
(1984).
\newblock The Valuation of FDIC Deposit Insurance Using Option-pricing Estimates
\newblock {\em Journal of Money, Credit and Banking}, 16:446--60.
\bibitem[RONN, EHUD I. and VERMA, AVINASH K.]{RONN et al., 1986}
RONN, EHUD I. and VERMA, AVINASH K.
(1986).
\newblock Pricing Risk-Adjusted Deposit Insurance: An Option-Based Model
\newblock {\em Journal of Money, Credit and Banking}, 41:871--895.
\bibitem[Laeven and Luc]{Laeven et al., 2002}
Laeven, Luc.
(2002).
\newblock Bank Risk and Deposit Insurance
\newblock {\em The World Bank Economic Review}, 16:109--137.
\bibitem[Falkenheim, Michael and Pennacchi, George]{Falkenheim et al., 2003}
Falkenheim, Michael and Pennacchi, George.
(2003).
\newblock The cost of deposit insurance for privately held banks: A market comparable approach
\newblock {\em Journal of Financial Services Research}, 24:121--148.
\end{thebibliography}

%----------------------------------------------------------------------------------------

\end{document}
